Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Proof-of-Concept V}}

### 2014-05-06 Paper.tex
Minor PoC-5 protocol changes.

The function $L_B$ and $L_H$ are the preparation functions for a block and block header respectively. Much like the transaction receipt preparation function $L_R$, we assert the types and order of the structure for when the RLP transformation is required:
\begin{eqnarray}
\quad L_H(H) & \equiv & (H_p, H_u, H_b, H_r, H_t, H_d, H_s, H_x, H_n) \\
\quad L_B(B) & \equiv & \big( L_H(B_H), L_R^*(B_\mathbf{R}), L_H^*(B_\mathbf{U}) \big)
\end{eqnarray}

@@

The account's nonce is initially defined as zero, the balance as the value passed, the storage as empty and the code hash as the SHA3 256-bit hash of the empty string, thus the mutated state becomes $\boldsymbol{\sigma}^*$:
\begin{eqnarray}
\boldsymbol{\sigma}^* & \equiv & \boldsymbol{\sigma} \quad \text{except:} \\
\boldsymbol{\sigma}^*[A(s, \boldsymbol{\sigma}[s]_n)] & \equiv & \big( 0, v, \mathtt{\tiny TRIE}(\varnothing), \mathtt{\tiny SHA3}\big(()\big) \big)
\end{eqnarray}

It is asserted that the state database will also change such that it defines the pair $(\mathtt{\tiny SHA3}(\mathbf{b}), \mathbf{b})$.

@@

If such an exception does not occur, then the remaining gas is refunded to the originator and the now-altered state is allowed to persevere. Thus formally, we may specify the resultant state and gas as $(\boldsymbol{\sigma}_P, g')$ where:
\begin{equation}
(\boldsymbol{\sigma}^{**}, g', \mathbf{o}) \equiv \Xi(\boldsymbol{\sigma}^*, g, I) \\
\end{equation}
\begin{eqnarray}
\quad \boldsymbol{\sigma}_P & \equiv & \begin{cases}
\boldsymbol{\sigma}_0 & \text{if} \quad \mathbf{o} = () \\
\begin{array}[b]{l}
\boldsymbol{\sigma}^{**} \quad \text{except:} \\
\boldsymbol{\sigma}_P[A(s, \boldsymbol{\sigma}[s]_n)]_{\mathbf{b}} = \mathbf{o}
\end{array} & \text{otherwise}
\end{cases} \\
I_a & \equiv & a \\
I_o & \equiv & s \\
I_p & \equiv & p \\
I_\mathbf{d} & \equiv & () \\
I_s & \equiv & s \\
I_v & \equiv & v \\
I_\mathbf{b} & \equiv & \mathbf{i}
\end{eqnarray}

@@

\subsection{Subtleties}
Note that while the initialisation code is executing, the newly created address exists but with no intrinsic body code. Thus any message call received by it during this time causes no code to be executed. If the initialisation execution ends with a {\small SUICIDE} instruction or normal {\small STOP} code, or if the code returned is otherwise empty, then the state changes are effectively reverted, the final state being equivalent to $\boldsymbol{\sigma}_0$, the pre-execution checkpoint state.

@@

The machine does not follow the standard von Neumann architecture. Rather than storing program code in memory or storage, it is stored separately in a virtual ROM. It cannot be read directly; instead it exists only as a model for determining the next instruction to execute.

>>>>

The function $L_B$ and $L_H$ are the preparation functions for a block and block header respectively. Much like the transaction receipt preparation function $L_R$, we assert the types and order of the structure for when the RLP transformation is required:
\begin{eqnarray}
\quad L_H(H) & \equiv & (\begin{array}[t]{l}H_p, H_u, H_b, H_r, H_t, H_d, H_s,\\ H_i, H_m, H_l, H_u, H_x, H_n \; )\end{array} \\
\quad L_B(B) & \equiv & \big( L_H(B_H), L_R^*(B_\mathbf{R}), L_H^*(B_\mathbf{U}) \big)
\end{eqnarray}

@@

The account's nonce is initially defined as zero, the balance as the value passed, the storage as empty and the code hash as the SHA3 256-bit hash of the empty string, thus the mutated state becomes $\boldsymbol{\sigma}^*$:
\begin{eqnarray}
\boldsymbol{\sigma}^* & \equiv & \boldsymbol{\sigma} \quad \text{except:} \\
\boldsymbol{\sigma}^*[a] & \equiv & \big( 0, v, \mathtt{\tiny TRIE}(\varnothing), \mathtt{\tiny SHA3}\big(()\big) \big)
\end{eqnarray}

where $a$ is the address of the new account, as defined above. It is asserted that the state database will also change such that it defines the pair $(\mathtt{\tiny SHA3}(\mathbf{b}), \mathbf{b})$.

@@

If such an exception does not occur, then the remaining gas is refunded to the originator and the now-altered state is allowed to persevere. Thus formally, we may specify the resultant state and gas as $(\boldsymbol{\sigma}_P, g')$ where:
\begin{equation}
(\boldsymbol{\sigma}^{**}, g', \mathbf{o}) \equiv \Xi(\boldsymbol{\sigma}^*, g, I) \\
\end{equation}
\begin{eqnarray}
\quad \boldsymbol{\sigma}_P & \equiv & \begin{cases}
\boldsymbol{\sigma}^{**} & \text{if} \quad \boldsymbol{\sigma}^{**}[a] = \varnothing \\
\begin{array}[b]{l}
\boldsymbol{\sigma}^{**} \quad \text{except:} \\
\boldsymbol{\sigma}_P[a]_{\mathbf{b}} = \mathbf{o}
\end{array} & \text{otherwise}
\end{cases} \\
I_a & \equiv & a \\
I_o & \equiv & s \\
I_p & \equiv & p \\
I_\mathbf{d} & \equiv & () \\
I_s & \equiv & s \\
I_v & \equiv & v \\
I_\mathbf{b} & \equiv & \mathbf{i}
\end{eqnarray}

@@

\subsection{Subtleties}
Note that while the initialisation code is executing, the newly created address exists but with no intrinsic body code. Thus any message call received by it during this time causes no code to be executed. If the initialisation execution ends with a {\small SUICIDE} instruction, no code is set. For a normal {\small STOP} code, or if the code returned is otherwise empty, then the state is left with a zombie account, and any remaining balance will be locked into the account forever.

@@

The machine does not follow the standard von Neumann architecture. Rather than storing program code in generally-accessible memory or storage, it is stored in a separately in a virtual ROM interactable only though a specialised instruction.
